\huge{Comment on `The Limits of Cosmic Shear'}

### 2016-12-04 conclusion.tex
Added a comment.
Added a conclusion paragraph about photo-z.

>>>>

\blue{The treatment of photo-$z$ uncertainties in \cite{kitching/etal:2016} is based on a simple linear shift of redshift distributions. This has been shown to be insufficient to capture the full complexity of the problem. More importantly though, it seems like \cite{kitching/etal:2016} apply the photo-$z$ calibrations from \cite{choi/etal:2016} in the wrong direction. Instead of alleviating the tension between CFHTLenS and Planck a correct application of the offsets would increase the discrepancy, in agreement with a recent re-analysis of the CFHTLenS data \citep{joudaki/etal:2016} as well as results from the KiDS project \citep{hildebrandt/etal:2016}.}
